SDR enhancement by clouds

### 2024-03-20 GHI_enh_04_investigate.tex
Commit 2024-03-20 12:14
Commit 2024-03-20 13:12

\begin{verbatim}
Warning: Removed 5 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 5 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

@@

\begin{verbatim}
2024-03-20 09:08:51.3 athan@tyler GHI_enh_04_investigate.R 1.076711 mins
\end{verbatim}

>>>>

\begin{verbatim}
Warning: Removed 12 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 2 rows containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 12 rows containing non-finite outside the scale range (`stat_bin2d()`).
Removed 2 rows containing missing values or values outside the scale range (`geom_tile()`).
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-3} \end{center}

@@

\begin{verbatim}
2024-03-20 09:43:30.5 athan@tyler GHI_enh_04_investigate.R 1.065564 mins
\end{verbatim}

### 2024-03-20 article/article.Rmd
Commit 2024-03-20 13:12

In order to further study the characteristics of the CE events, we grouped the singe
minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
successive CE cases, and can have a duration of multiple of minutes.  We have
identified `r ST_G0[, .N]` groups, where the group with the longest duration lasted
`r ST_G0[, max(GLB_diff.N)]` minutes on 
`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), is evident that durations above
10 minutes are very rare.

@@

<!-- Change color -->

```{r echo=FALSE, fig.cap="Distribution of the number of ECE cases"}
knitr::include_graphics("../images/climECEmonth-1.png")
```

>>>>

In order to further study the characteristics of the CE events, we grouped the singe
minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
successive CE cases, and can have a duration of multiple of minutes.  We have
identified `r ST_G0[, .N]` groups, where the group with the longest duration lasted
`r ST_G0[, max(GLB_diff.N)]` minutes on 
`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude that longer durations are getting increasingly rare, with durations above 10 minutes very rare.

@@

Another aspect of the CE events are the cases where the irradiance is above the expected irradiance on top of the atmosphere, we have defined this

<!-- ```{r echo=FALSE, fig.cap="Distribution of the number of ECE cases"} -->
<!-- knitr::include_graphics("../images/climECEmonth-1.png") -->
<!-- ``` -->

### 2024-03-20 article/article.tex
Commit 2024-03-20 13:12

In order to further study the characteristics of the CE events, we grouped the singe
minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
successive CE cases, and can have a duration of multiple of minutes. We have
identified 29009 groups, where the group with the longest duration lasted
140 minutes on
07~July 2013.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), is evident that durations above
10 minutes are very rare.

@@

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/climECEmonth-1}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-6}
\end{figure}

>>>>

In order to further study the characteristics of the CE events, we grouped the singe
minute CE events, to continuous CE groups (CEG). Thus, a CEG consists of one or more
successive CE cases, and can have a duration of multiple of minutes. We have
identified 29009 groups, where the group with the longest duration lasted
140 minutes on
07~July 2013.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can conclude that longer durations are getting increasingly rare, with durations above 10 minutes very rare.

@@

Another aspect of the CE events are the cases where the irradiance is above the expected irradiance on top of the atmosphere, we have defined this

@@

@@

\caption{Distribution of }\label{fig:unnamed-chunk-4}
\end{figure}

@@
